---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aeolus

<!-- badges: start -->
[![R-CMD-check](https://github.com/maelle/aeolus/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/maelle/aeolus/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of aeolus is to create better, more semantic linebreaks in your Markdown file.
aEOLus, get it? :wink:

## Installation

You can install the development version of aeolus like so:

``` r
pak::pak("maelle/aeolus")
```

## Why have semantic linebreaks?

For any Markdown parser the two following code chunks are the same:

```md
This is a sentence. This is another
sentence.
```

```md
This is a sentence. 
This is another sentence.
```

However, the second one will make your work easier when you use version control.
Git treats code by **line** so if lines are logical units as opposed to random units
or units of a certain length, 
the Git diff is better. 

If you change one sentence in a paragraph, and that paragraph is a single line, 
the Git diff is less readable.

With semantic linebreaks, code suggestions in GitHub Pull Requests are easier to make and use.

More information: <https://sembr.org/>.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(aeolus)
markdown_file <- system.file("example.md", package = "aeolus")
readLines(markdown_file)
unleash(markdown_file)
readLines(markdown_file)
```
